corpus download and clean

### 2022-07-22 replication_corpus/rmd/download_and_clean.Rmd

fromscratch=F
if(fromscratch){
  urls <- readLines("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/sheet1.xml.rels")[[2]] %>%
    str_replace_all("Target=","\n") %>%
    str_replace_all("TargetMode=","\n") %>%  
    str_replace_all("Type=","\n") %>%
    str_split("\n") %>% unique() %>%
    as.data.frame() %>% setNames("V1") %>% 
    filter(!V1 %>% str_detect("hyperlink|External|Relationships")) %>%
    mutate(V1 = V1 %>% str_replace_all('\"','') %>% trimws() )
  urls$V1 %>% sapply(FUN= function(x) try({ drive_download(x) })  )
  #Google drive download
  library("googledrive")
  #https://drive.google.com/open?id=186JCTWqxQCCRBbLl0JDzeFEpJxijoyoB 
  setwd("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/crisis_texts/")
  getwd()
  temp <- drive_download(file="https://drive.google.com/open?id=186JCTWqxQCCRBbLl0JDzeFEpJxijoyoB" ) # type = "csv",
}
#Nope the original csv files are broken. I'm going to have to reparse them from the website
#icb_long  %>%
#  dplyr::select(sentence_hash) %>% distinct() %>% View()
#There are 4 not in the icb long #397 403 451 459 474
setdiff(1:476, icb_long %>% dplyr::filter(varname=="crisno") %>% dplyr::pull(value) %>% unique() %>% as.numeric() %>% sort())
icb_crisis_summaries_20150604 <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/icb_crisis_summaries_20150604.csv")
icb_crisis_summaries_20150604_handadditions <- read_csv("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/icb_crisis_summaries_20150604_handadditions.csv") #this gets us 1 to 455
icb_crisis_summaries <- bind_rows(icb_crisis_summaries_20150604,icb_crisis_summaries_20150604_handadditions) %>%
  mutate(background = background %>% stringi::stri_enc_toutf8(validate=T)) %>% #there are non utf-8 characters
  mutate(text = text %>% stringi::stri_enc_toutf8(validate=T))

@@

#Note I had to manually recreate the 001 crisis because it was just a dump of a large text file containing first 200ish crises
files <- list.files(path = "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/in/crisis_texts/", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE)

filed_df <- data.frame(file=files) %>%
            mutate(filetype=NA) %>%
            mutate(filetype=ifelse(file %>% str_detect("pdf$"), "pdf", filetype)) %>%
            mutate(filetype=ifelse(file %>% str_detect("txt$"), "txt", filetype)) %>%
            mutate(filetype=ifelse(file %>% str_detect("docx$"), "docx", filetype)) %>%
            mutate(text=NA)
n=nrow(filed_df)
path <- "/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/in/crisis_texts/"
library(pdftools)
library(textreadr)
for(i in 1:n){
  if(filed_df$filetype[i]=="txt"){
    filed_df$text[i] <- path %>% paste0(filed_df$file[i]) %>% readLines() %>% paste0(collapse="\n") %>% str_replace_all("\n",' ')
  }
  if(filed_df$filetype[i]=="docx"){
    filed_df$text[i] <- path %>% paste0(filed_df$file[i])  %>% read_docx() %>% paste0(collapse="\n") %>% str_replace_all("\n",' ')
  }
  if(filed_df$filetype[i]=="pdf"){
    filed_df$text[i] <- path %>% paste0(filed_df$file[i])  %>% pdftools::pdf_text() %>% str_replace_all("1\n|2\n|3\n|4\n",' ') %>% paste0(collapse="\n") %>% str_replace_all("\n",' ')
  }
}

@@

icb_corpus %>% saveRDS("/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_corpus/data/out/icb_corpus_V1.0_May_16_2022.Rds")

>>>>

fromscratch=F
if(fromscratch){
  urls <- readLines(here::here("replication_data", "in", "sheet1.xml.rels"))[[2]] %>%
    str_replace_all("Target=","\n") %>%
    str_replace_all("TargetMode=","\n") %>%  
    str_replace_all("Type=","\n") %>%
    str_split("\n") %>% unique() %>%
    as.data.frame() %>% setNames("V1") %>% 
    filter(!V1 %>% str_detect("hyperlink|External|Relationships")) %>%
    mutate(V1 = V1 %>% str_replace_all('\"','') %>% trimws() )
  urls$V1 %>% sapply(FUN= function(x) try({ drive_download(x) })  )
  #Google drive download
  library("googledrive")
  #https://drive.google.com/open?id=186JCTWqxQCCRBbLl0JDzeFEpJxijoyoB 
  setwd(here::here("replication_data", "in", "crisis_texts"))
  getwd()
  temp <- drive_download(file="https://drive.google.com/open?id=186JCTWqxQCCRBbLl0JDzeFEpJxijoyoB" ) # type = "csv",
}
#Nope the original csv files are broken. I'm going to have to reparse them from the website
#icb_long  %>%
#  dplyr::select(sentence_hash) %>% distinct() %>% View()
#There are 4 not in the icb long #397 403 451 459 474
setdiff(1:476, icb_long %>% dplyr::filter(varname=="crisno") %>% dplyr::pull(value) %>% unique() %>% as.numeric() %>% sort())
icb_crisis_summaries_20150604 <- read_csv(here::here("replication_data", "in", "icb_crisis_summaries_20150604.csv"))

icb_crisis_summaries_20150604_handadditions <- read_csv(here::here("replication_data", "in", "icb_crisis_summaries_20150604_handadditions.csv")) #this gets us 1 to 455

icb_crisis_summaries <- bind_rows(icb_crisis_summaries_20150604,icb_crisis_summaries_20150604_handadditions) %>%
  mutate(background = background %>% stringi::stri_enc_toutf8(validate=T)) %>% #there are non utf-8 characters
  mutate(text = text %>% stringi::stri_enc_toutf8(validate=T))

@@

#Note I had to manually recreate the 001 crisis because it was just a dump of a large text file containing first 200ish crises

files <- list.files(path = here::here("replication_corpus", "data", "in", "crisis_texts/"), pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE, ignore.case = FALSE, include.dirs = FALSE)

filed_df <- data.frame(file=files) %>%
            mutate(filetype=NA) %>%
            mutate(filetype=ifelse(file %>% str_detect("pdf$"), "pdf", filetype)) %>%
            mutate(filetype=ifelse(file %>% str_detect("txt$"), "txt", filetype)) %>%
            mutate(filetype=ifelse(file %>% str_detect("docx$"), "docx", filetype)) %>%
            mutate(text=NA)
n=nrow(filed_df)
path <- here::here("replication_corpus", "data", "in", "crisis_texts/")
library(pdftools)
library(textreadr)
for(i in 1:n){
  if(filed_df$filetype[i]=="txt"){
    filed_df$text[i] <- path %>% paste0(filed_df$file[i]) %>% readLines() %>% paste0(collapse="\n") %>% str_replace_all("\n",' ')
  }
  if(filed_df$filetype[i]=="docx"){
    filed_df$text[i] <- path %>% paste0(filed_df$file[i])  %>% read_docx() %>% paste0(collapse="\n") %>% str_replace_all("\n",' ')
  }
  if(filed_df$filetype[i]=="pdf"){
    filed_df$text[i] <- path %>% paste0(filed_df$file[i])  %>% pdftools::pdf_text() %>% str_replace_all("1\n|2\n|3\n|4\n",' ') %>% paste0(collapse="\n") %>% str_replace_all("\n",' ')
  }
}

@@

icb_corpus %>% saveRDS(here::here("replication_corpus", "data", "out", "icb_corpus_V1.0_May_16_2022.Rds"))
